Regional Base-Flow Index in Arid Landscapes Using Machine Learning and Instrumented Records

### 2025-04-04 elsevier_MANUSCRIPT.qmd
updated figures

![Map of Arizona and US Geological Survey (USGS) streamgages used in this study. 8-digit HUC subbasin boundaries and physiographic regions shown.](images/StudyArea_20241203.png){#fig-study-area}

@@

![Long-term BFI for the period of record from instrumented stream flow data.](images/BFI_Instrumented_20241203.png){#fig-instrumented-bfi}

@@

![Trends in BFI over full period of record for instrumented sites used in this study. Red upward (blue downward) arrows indicate an increasing (decreasing) trend at a significance level of 5%. White circles represent sites with no statistically significant trends.](images/BFITrends_20241203.png){#fig-instrumented-trend}

@@

![Predicted long-term BFI values for 8-digit HUC (1991-2020)](images/BFI_HUC8_20250129.png){#fig-bfi-huc}

>>>>

![Map of Arizona and US Geological Survey (USGS) streamgages used in this study. 8-digit HUC subbasin boundaries and physiographic regions shown.](images/updated/StudyArea_20250404.png){#fig-study-area}

@@

![Long-term BFI for the period of record from instrumented stream flow data.](images/updated/BFI_Instrumented_20240404.png){#fig-instrumented-bfi}

@@

![Trends in BFI over full period of record for instrumented sites used in this study. Red upward (blue downward) arrows indicate an increasing (decreasing) trend at a significance level of 5%. White circles represent sites with no statistically significant trends.](images/updated/BFITrends_20250404.png){#fig-instrumented-trend}

@@

![Predicted long-term BFI values for 8-digit HUC (1991-2020)](images/updated/BFI_HUC8_20250404.png){#fig-bfi-huc}
